---
title: "Data processing pipeline"
---

This page provides the code that has been used in data processing and generating the figures.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r packages, message=FALSE, warning=FALSE}
library(readr)
library(stringr)
library(dplyr)
library(tidyr)
library(kableExtra)
```

## Data cleaning
A basic data clearning function, to derive necessary variables.
```{r data cleaning functions}
data.clean <- function(dataframe){
  dataframe <- dataframe %>%
    mutate(
    dia = str_extract(filename,"diaN?[1-2]?n?"),
    condition = str_split_i(filename, "diaN?[1-2]?n?",-1),
    focus = str_sub(filename,-1,-1),
    tone = str_sub(condition,1,str_length(condition)-1),
    participant = str_extract(filename, "S[0-9]+"),
    char_duration = maxTime - minTime,
    tone = as.factor(tone),
    focus = as.factor(focus),
    participant = as.factor(participant)
  )
}
```

The initial data, after applying the cleaning function, is shown below (first 200 rows are shown).
```{r}
changsha.raw <- read_tsv("./data/Changsha_data.tsv", col_names = TRUE,show_col_types = FALSE)
changsha.clean <- data.clean(changsha.raw)

changsha.clean %>%
  head(200) %>%
  kable(format = "html", col.names = colnames(changsha.clean)) %>%
  kable_styling() %>%
  kableExtra::scroll_box(width = "100%", height = "300px")
```


We then did several data transformations to convert f0 to semitone scale and calculate the f0 difference at each normalised time points.
```{r}
# Add a new variable for the last word in the sentence
changsha.clean <- changsha.clean %>%
  group_by(filename) %>%
  mutate(
    boundary = if_else(idx == max(idx, na.rm = TRUE),1,0)
  ) %>%
  ungroup()

# Transform to long format, and generate f0 in semintone scale
changsha.long_initial <- changsha.clean %>%
  pivot_longer(cols = matches('t[0-9]+', ignore.case = FALSE), names_to = "Time",names_prefix = "t", values_to = "f0") %>% # Convert to the standard long format
  group_by(participant) %>%
  mutate(
    f0ref = mean(f0, na.rm = T),
    f0_semi = 12*log(f0/f0ref,2)
  ) %>%
  ungroup()

# Transform to wide format and calculate the difference between conditions
changsha.wide <- changsha.long_initial %>% 
  select(-minTime, -maxTime,-condition,-rhyme_duration,-f0min,-f0max,-f0min_time,-f0max_time) %>%
  pivot_wider(id_cols = c("idx","boundary", "rhyme", "case","participant","dia", "tone","Time"),
    names_from = focus,
    names_prefix = "F",
    values_from = f0_semi) %>%
  mutate(F2_1 = F2-F1,
         F5_1 = F5-F1,
         F2_5 = F2-F5) 

# Transfrom to long format
changsha.long <- changsha.wide %>%
  pivot_longer(
      cols = starts_with("F"),
      names_to = "FocusCon",
      values_to = "F0_semi"
    )

# For plotting, we need to revert back to long format again
changsha.long.sen <- changsha.long %>%
  filter(idx ==1 | idx == 2 | idx ==3 | idx ==4 |idx ==5 |idx == 6 | idx == 7) %>%
  mutate(
    Time = as.numeric(Time),
    case = factor(case,levels=c("Name(prefix)","Name","Verb","Aspect", "Classifier", "Object","Object(suffix)")),
    FocusCon = factor(FocusCon, levels = c("F1","F2","F5","F2_1","F5_1","F2_5")),
    tone = factor(tone, levels = c("A","B","C","D","F"), labels = c("T1","T2","T3","T4","T6")),
    underfocus = case_when(
      FocusCon == "F2" & case == "Name" ~ 1,
      FocusCon == "F5" & case == "Object" ~ 1,
      TRUE ~ 0
    ),
    underfocus = as.factor(underfocus)
  ) %>%
  group_by(idx, Time, FocusCon) %>%
  mutate(
    F0_semi_scale = F0_semi-mean(F0_semi)
  ) %>%
  ungroup()

changsha.long.sen %>%
  head(200) %>%
  kable(format = "html", col.names = colnames(changsha.long.sen)) %>%
  kable_styling() %>%
  kableExtra::scroll_box(width = "100%", height = "300px")
```


## Data visualisation

The function below is used in plotting the figures in the demo pages.
```{r visualisation functions, message=FALSE, warning=FALSE}
case.labs <- c("Prefex", "Name", "Verb", "Aspect","Classfier","Object","Suffix")
names(case.labs) <- c("Name(prefix)","Name","Verb","Aspect", "Classifier", "Object","Object(suffix)")
rawplot <- function(data){
    ggplot(data, aes(x = Time, y = F0_semi, group = FocusCon,color = FocusCon, linetype = FocusCon, linewidth = underfocus)) +
    stat_summary(fun = mean, geom = "smooth") +
    scale_color_manual(name = "Focus condition",
                       breaks = c("F2","F5"),
                       labels = c("Subject focus","Object focus"),
                       values = c("#6a4cb5","#E69F00")) +
    scale_linetype_manual(name = "Focus condition",
                       breaks = c("F2","F5"),
                       labels = c("Subject focus","Object focus"),
                       values = c("solid","dashed")) +
    scale_linewidth_manual(name = "Focused",
                      breaks = c("0","1"),
                      labels = c("Normal","Focused"),
                      values = c(0.8,1.3),
                      guide = "none") +
    facet_grid(tone~case, labeller = labeller(case = case.labs)) + 
    labs(x="Normalized Time point", y = "F0 in semitone") +
    theme_bw() +
    theme(axis.title = element_text(size = 10), 
        legend.title = element_text (size =12), 
        legend.text = element_text(size = 15),
        legend.position = "bottom",
        plot.title = element_text(size=15),
        strip.text = element_text(size = 15))
}
diffplot <- function(data){
    data_average <- data %>%
    group_by(FocusCon, tone, case,Time) %>%
    summarise(F0_semi = mean(F0_semi))
  ggplot(data, aes(x = Time, y = F0_semi, group = FocusCon,color = FocusCon)) +
  geom_hline(yintercept = 0,color = "#000000") + 
    stat_summary(fun = mean, geom = "smooth") +
    geom_area(data = subset(data_average), fill = "#C54e4f", alpha=0.6) +
  scale_color_manual(name = "Focus condition",
                       breaks = c("F2_5"),
                       labels = c( "Suibject-Object"),
                       values = c("#C54e4f")) +
    facet_grid(tone~case,labeller = labeller(case = case.labs)) + 
    scale_linetype_manual(name = "Focus condition",
                       breaks = c("F2_5"),
                       labels = c("Suibject-Object"),
                       values = c("solid")) +
  theme_bw()+
  labs(x="Normalized Time point", y = "F0 in semitone") +
  theme(axis.title = element_text(size = 10), 
        legend.title = element_blank(), #element_text (size =12), 
        legend.text = element_text(size = 15),
        legend.position = "bottom",
        plot.title = element_text(size=15),
        strip.text = element_text(size = 15))
}