---
title: "Demo in Chengdu"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(ggplot2)
library(lingglosses)
```

```{r include = FALSE}
html_tag_audio <- function(file,
                           type = "wav")
{
  htmltools::tags$audio(controls = NA,
                        htmltools::tags$source(src = file,
                                               type = glue::glue("audio/{type}",
                                                                 type = type)))
}
# source: https://community.rstudio.com/t/audio-files-in-r-markdown/20874/4
```

```{r visualisation functions, include=FALSE}
case.labs <- c("Prefex", "Name", "Verb", "Aspect","Classfier","Object","Suffix")
names(case.labs) <- c("Name(prefix)","Name","Verb","Aspect", "Classifier", "Object","Object(suffix)")
rawplot <- function(data){
    ggplot(data, aes(x = Time, y = F0_semi, group = FocusCon,color = FocusCon, linetype = FocusCon, linewidth = underfocus)) +
    stat_summary(fun = mean, geom = "smooth") +
    scale_color_manual(name = "Focus condition",
                       breaks = c("F2","F5"),
                       labels = c("Subject focus","Object focus"),
                       values = c( "#56B4E9","#E69F00")) +
    scale_linetype_manual(name = "Focus condition",
                       breaks = c("F2","F5"),
                       labels = c("Subject focus","Object focus"),
                       values = c("solid","dashed")) +
    scale_linewidth_manual(name = "Focused",
                      breaks = c("0","1"),
                      labels = c("Normal","Focused"),
                      values = c(0.8,1.3),
                      guide = "none") +
    facet_grid(tone~case, labeller = labeller(case = case.labs)) + 
    labs(x="Normalized Time point", y = "F0 in semitone") +
    theme_bw() +
    theme(axis.title = element_text(size = 10), 
        legend.title = element_text (size =12), 
        legend.text = element_text(size = 15),
        legend.position = "bottom",
        plot.title = element_text(size=15),
        strip.text = element_text(size = 15))
}
diffplot <- function(data){
  ggplot(data, aes(x = Time, y = F0_semi, group = FocusCon,color = FocusCon)) +
  geom_hline(yintercept = 0,color = "red") + 
    stat_summary(fun = mean, geom = "smooth") +
  scale_color_manual(name = "Focus condition",
                       breaks = c("F2_5"),
                       labels = c( "Suibject-Object"),
                       values = c("#000000")) +
    facet_grid(tone~case,labeller = labeller(case = case.labs)) + 
    scale_linetype_manual(name = "Focus condition",
                       breaks = c("F2_5"),
                       labels = c("Suibject-Object"),
                       values = c("solid")) +
  theme_bw()+
  labs(x="Normalized Time point", y = "F0 in semitone") +
  theme(axis.title = element_text(size = 10), 
        legend.title = element_blank(), #element_text (size =12), 
        legend.text = element_text(size = 15),
        legend.position = "bottom",
        plot.title = element_text(size=15),
        strip.text = element_text(size = 15))
}
```

In the provided transcriptions, the tones are represented using Chao numbers, with 1 indicates the lowest pitch, and 5 indicates the highest pitch.

The curve below represents three repetitions of one participant in each language.

The four tones of Chengdu are: T1[35], T2[31], T3[53], T4[13]

```{r Read chengdu data, include=FALSE}
chengdu.long.sen <- read.csv("./data/chengdu_long_sen.csv")
chengdu.long.sen <- chengdu.long.sen %>%
  mutate(
    case = factor(case,levels=c("Name(prefix)","Name","Verb","Aspect", "Classifier", "Object","Object(suffix)")),
    tone = as.factor(tone),
    FocusCon = as.factor(FocusCon),
    underfocus = as.factor(underfocus),
    participant = as.factor(participant),
    dia = as.factor(dia)
  )
str(chengdu.long.sen)
chengdu.raw.figure <- chengdu.long.sen %>%
  filter(FocusCon != "F2_1" & FocusCon != "F5_1" & FocusCon != "F2_5" & FocusCon != "F1")
chengdu.diff.figure <- chengdu.long.sen %>%
  filter(FocusCon == "F2_5")
```

## T1
:::: {style="display: grid; grid-template-columns: 1fr 1fr; grid-column-gap: 10px;"}
::: {}
```{r echo=FALSE}
gloss_example(transliteration = "ɕiaʊ53 **jɪər35** **niɛ35** lə0 kə23 **sʐ35** tsɹ0",
              glosses = "Name_prefix Name Verb Aspect Classifier Object Object_Suffix",
              free_translation = "Xiao-yin made a lion (out of mud).",
              annotation = "小 英儿 捏 了 个 狮 子")
```
:::
:::{}
Subject focus (blue line)        `r html_tag_audio("Audiofiles_wav/Chengdu-T1-Subj.wav")`

Object focus (orange line)     `r html_tag_audio("Audiofiles_wav/Chengdu-T1-Obj.wav")`
:::
::::



:::: {style="display: grid; grid-template-columns: 1fr 1fr; grid-column-gap: 10px;"}
::: {}

```{r echo=FALSE, message=FALSE, warning=FALSE}
rawplot(subset(chengdu.raw.figure, tone == "T1"))
```
:::

::: {}

```{r echo=FALSE, message=FALSE, warning=FALSE}
diffplot(subset(chengdu.diff.figure, tone == "T1"))
```

:::
::::

## T2
:::: {style="display: grid; grid-template-columns: 1fr 1fr; grid-column-gap: 10px;"}
::: {}
```{r echo=FALSE}
gloss_example(transliteration = "ɕiaʊ53 **jɪn31** **na31** lə0 kə23 **læ31** tsɹ0",
              glosses = "Name_prefix Name Verb Aspect Classifier Object Object_Suffix",
              free_translation = "Xiao-yin brought a basket.",
              annotation = "小 银 拿 了 个 篮 子")
```
:::

::: {}
Subject focus (blue line)       `r html_tag_audio("Audiofiles_wav/Chengdu-T2-Subj.wav")`

Object focus (orange line)     `r html_tag_audio("Audiofiles_wav/Chengdu-T2-Obj.wav")`
:::
::::

:::: {style="display: grid; grid-template-columns: 1fr 1fr; grid-column-gap: 10px;"}
::: {}

```{r echo=FALSE, message=FALSE, warning=FALSE}
rawplot(subset(chengdu.raw.figure, tone == "T2"))
```
:::

::: {}

```{r echo=FALSE, message=FALSE, warning=FALSE}
diffplot(subset(chengdu.diff.figure, tone == "T2"))
```

:::
::::

## T3
:::: {style="display: grid; grid-template-columns: 1fr 1fr; grid-column-gap: 10px;"}
::: {}
```{r echo=FALSE}
gloss_example(transliteration = "ɕiaʊ53 **jɪn53** **mai53** lə0 pa53 **ji53** tsɹ0",
              glosses = "Name_prefix Name Verb Aspect Classifier Object Object_Suffix",
              free_translation = "Xiao-yin bought a chair.",
              annotation = "小 影 买 了 把 椅 子")
```
:::

::: {}
Subject focus (blue line)       `r html_tag_audio("Audiofiles_wav/Chengdu-T3-Subj.wav")`


Object focus (orange line)      `r html_tag_audio("Audiofiles_wav/Chengdu-T3-Obj.wav")`
:::
::::

:::: {style="display: grid; grid-template-columns: 1fr 1fr; grid-column-gap: 10px;"}
::: {}

```{r echo=FALSE, message=FALSE, warning=FALSE}
rawplot(subset(chengdu.raw.figure, tone == "T3"))
```
:::

::: {}

```{r echo=FALSE, message=FALSE, warning=FALSE}
diffplot(subset(chengdu.diff.figure, tone == "T3"))
```

:::
::::

## T4
:::: {style="display: grid; grid-template-columns: 1fr 1fr; grid-column-gap: 10px;"}
::: {}
```{r echo=FALSE}
gloss_example(transliteration = "ɕiaʊ53 **jɪn23** **mai23** lə0 suaŋ35 **ua23** tsɹ0",
              glosses = "Name_prefix Name Verb Aspect Classifier Object Object_Suffix",
              free_translation = "Xiao-yin sold a pair of socks.",
              annotation = "小 映 卖 了 双 袜 子")
```
:::

::: {}
Subject focus (blue line)      `r html_tag_audio("Audiofiles_wav/Chengdu-T4-Subj.wav")`

Object focus (orange line)       `r html_tag_audio("Audiofiles_wav/Chengdu-T4-Obj.wav")`
:::
::::

:::: {style="display: grid; grid-template-columns: 1fr 1fr; grid-column-gap: 10px;"}
::: {}

```{r echo=FALSE, message=FALSE, warning=FALSE}
rawplot(subset(chengdu.raw.figure, tone == "T4"))
```
:::

::: {}

```{r echo=FALSE, message=FALSE, warning=FALSE}
diffplot(subset(chengdu.diff.figure, tone == "T4"))
```

:::
::::


## Chengdu combined

The above four figures are combined with the same f0 range on y-axis.

```{r include=FALSE}
remove_y <- theme(
  axis.title.y = element_blank()
  # axis.ticks.y = element_blank(),
  # axis.text.y = element_blank()
)
chengdu.raw <- rawplot(chengdu.raw.figure) + theme(strip.text.y = element_blank())
chengdu.diff <- diffplot(chengdu.diff.figure) + remove_y
```


:::: {style="display: grid; grid-template-columns: 1fr 1fr; grid-column-gap: 10px;"}
::: {}

```{r echo=FALSE, message=FALSE, warning=FALSE}
chengdu.raw
```
:::

::: {}

```{r echo=FALSE, message=FALSE, warning=FALSE}
chengdu.diff
```

:::
::::