---
title: "Demo in Changsha"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(ggplot2)
library(lingglosses)
```

```{r include = FALSE}
html_tag_audio <- function(file,
                           type = "wav")
{
  htmltools::tags$audio(controls = NA,
                        htmltools::tags$source(src = file,
                                               type = glue::glue("audio/{type}",
                                                                 type = type)))
}
# source: https://community.rstudio.com/t/audio-files-in-r-markdown/20874/4
```

```{r visualisation functions, message=FALSE, warning=FALSE, include=FALSE}
case.labs <- c("Prefix", "Name", "Verb", "Aspect","Classfier","Object","Suffix")
names(case.labs) <- c("Name(prefix)","Name","Verb","Aspect", "Classifier", "Object","Object(suffix)")
rawplot <- function(data){
    ggplot(data, aes(x = Time, y = F0_semi, group = FocusCon,color = FocusCon, linetype = FocusCon, linewidth = underfocus)) +
    stat_summary(fun = mean, geom = "smooth") +
    scale_color_manual(name = "Focus condition",
                       breaks = c("F2","F5"),
                       labels = c("Subject focus","Object focus"),
                       values = c("#6a4cb5","#E69F00")) +
    scale_linetype_manual(name = "Focus condition",
                       breaks = c("F2","F5"),
                       labels = c("Subject focus","Object focus"),
                       values = c("solid","dashed")) +
    scale_linewidth_manual(name = "Focused",
                      breaks = c("0","1"),
                      labels = c("Normal","Focused"),
                      values = c(0.8,1.3),
                      guide = "none") +
    facet_grid(tone~case, labeller = labeller(case = case.labs)) + 
    labs(x="Normalized Time point", y = "F0 in semitone") +
    theme_bw() +
    theme(axis.title = element_text(size = 10), 
        legend.title = element_text (size =12), 
        legend.text = element_text(size = 15),
        legend.position = "bottom",
        plot.title = element_text(size=15),
        strip.text = element_text(size = 15))
}
diffplot <- function(data){
    data_average <- data %>%
    group_by(FocusCon, tone, case,Time) %>%
    summarise(F0_semi = mean(F0_semi))
  ggplot(data, aes(x = Time, y = F0_semi, group = FocusCon,color = FocusCon)) +
  geom_hline(yintercept = 0,color = "#000000") + 
    stat_summary(fun = mean, geom = "smooth") +
    geom_area(data = subset(data_average), fill = "#C54e4f", alpha=0.6) +
  scale_color_manual(name = "Focus condition",
                       breaks = c("F2_5"),
                       labels = c( "Suibject-Object"),
                       values = c("#C54e4f")) +
    facet_grid(tone~case,labeller = labeller(case = case.labs)) + 
    scale_linetype_manual(name = "Focus condition",
                       breaks = c("F2_5"),
                       labels = c("Suibject-Object"),
                       values = c("solid")) +
  theme_bw()+
  labs(x="Normalized Time point", y = "F0 in semitone") +
  theme(axis.title = element_text(size = 10), 
        legend.title = element_blank(), #element_text (size =12), 
        legend.text = element_text(size = 15),
        legend.position = "bottom",
        plot.title = element_text(size=15),
        strip.text = element_text(size = 15))
}
```

In the provided transcriptions, the tones are represented using Chao numbers, with 1 indicates the lowest pitch, and 5 indicates the highest pitch.

The curve below represents three repetitions of one participant in each language.

The four tones of Changsha are: T1[34], T2[13], T3[42], T4[45], with two more tones now included here T5 [21] and T6[13].

```{r Read changsha data, include=FALSE}
changsha.long.sen <- read.csv("./data/Changsha_long_sen.csv")
changsha.long.sen <- changsha.long.sen %>%
  mutate(
    case = factor(case,levels=c("Name(prefix)","Name","Verb","Aspect", "Classifier", "Object","Object(suffix)")),
    tone = as.factor(tone),
    FocusCon = as.factor(FocusCon),
    underfocus = as.factor(underfocus),
    participant = as.factor(participant),
    dia = as.factor(dia)
  )
str(changsha.long.sen)
changsha.raw.figure <- changsha.long.sen %>%
  filter(FocusCon != "F2_1" & FocusCon != "F5_1" & FocusCon != "F2_5" & FocusCon != "F1")
changsha.diff.figure <- changsha.long.sen %>%
  filter(FocusCon == "F2_5")
```

\

## T1

:::: {style="display: grid; grid-template-columns: 1fr 1fr; grid-column-gap: 10px;"}
::: {}
```{r echo=FALSE}
gloss_example(transliteration = "ɕiaʊ42 **jɪŋ34** **kʰai34** ta21 tsa34 **iɛ34** tsɹ33",
              glosses = "Name_prefix Name Verb Aspect Classifier Object Object_Suffix",
              free_translation = "Xiao-ying opened a coconut.",
              annotation = "小 英 开 哒 只 椰 子")
```
:::
:::{}
Subject focus (Purple line)        `r html_tag_audio("Audiofiles_wav/Changsha-T1-Subj.wav")`

Object focus (orange line)     `r html_tag_audio("Audiofiles_wav/Changsha-T1-Obj.wav")`
:::
::::



:::: {style="display: grid; grid-template-columns: 1fr 1fr; grid-column-gap: 10px;"}
::: {}

```{r echo=FALSE}
rawplot(subset(changsha.raw.figure, tone == "T1"))
```
:::

::: {}

```{r echo=FALSE}
diffplot(subset(changsha.diff.figure, tone == "T1"))
```

:::
::::

\

## T2
:::: {style="display: grid; grid-template-columns: 1fr 1fr; grid-column-gap: 10px;"}
::: {}
```{r echo=FALSE}
gloss_example(transliteration = "ɕiaʊ42 **jɪŋ13** **tia13** ta21 tsa34	**lan13** tsɹ33",
              glosses = "Name_prefix Name Verb Aspect Classifier Object Object_Suffix",
              free_translation = "Xiao-ying brought a basket.",
              annotation = "小 莹 提 哒 杂 篮 子")
```
:::
:::{}
Subject focus (purple line)        `r html_tag_audio("Audiofiles_wav/Changsha-T2-Subj.wav")`

Object focus (orange line)     `r html_tag_audio("Audiofiles_wav/Changsha-T2-Obj.wav")`
:::
::::



:::: {style="display: grid; grid-template-columns: 1fr 1fr; grid-column-gap: 10px;"}
::: {}

```{r echo=FALSE}
rawplot(subset(changsha.raw.figure, tone == "T2"))
```
:::

::: {}

```{r echo=FALSE}
diffplot(subset(changsha.diff.figure, tone == "T2"))
```

:::
::::

\

## T3

:::: {style="display: grid; grid-template-columns: 1fr 1fr; grid-column-gap: 10px;"}
::: {}
```{r echo=FALSE}
gloss_example(transliteration = "ɕiaʊ42 **jɪŋ42** **mɑi42** tɑ21 tsɑ34 **li42** tsɹ33 ",
              glosses = "Name_prefix Name Verb Aspect Classifier Object Object_Suffix",
              free_translation = "Xiao-ying bought a plum.",
              annotation = "小 影 买 哒 只 李 子")
```
:::
:::{}
Subject focus (purple line)        `r html_tag_audio("Audiofiles_wav/Changsha-T3-Subj.wav")`

Object focus (orange line)     `r html_tag_audio("Audiofiles_wav/Changsha-T3-Obj.wav")`
:::
::::


:::: {style="display: grid; grid-template-columns: 1fr 1fr; grid-column-gap: 10px;"}
::: {}

```{r echo=FALSE}
rawplot(subset(changsha.raw.figure, tone == "T3"))
```
:::

::: {}

```{r echo=FALSE}
diffplot(subset(changsha.diff.figure, tone == "T3"))
```

:::
::::

\

## T4

:::: {style="display: grid; grid-template-columns: 1fr 1fr; grid-column-gap: 10px;"}
::: {}
```{r echo=FALSE}
gloss_example(transliteration = "ɕiaʊ42 **jɪŋ45** **mɑi45** tɑ21 tsɑ34 **iou45** tsɹ33",
              glosses = "Name_prefix Name Verb Aspect Classifier Object Object_Suffix",
              free_translation = "Xiao-ying sold a grape fruit.",
              annotation = "小 映 卖 哒 只 柚 子")
```
:::
:::{}
Subject focus (purple line)        `r html_tag_audio("Audiofiles_wav/Changsha-T4-Subj.wav")`

Object focus (orange line)     `r html_tag_audio("Audiofiles_wav/Changsha-T4-Obj.wav")`
:::
::::



:::: {style="display: grid; grid-template-columns: 1fr 1fr; grid-column-gap: 10px;"}
::: {}

```{r echo=FALSE}
rawplot(subset(changsha.raw.figure, tone == "T4"))
```
:::

::: {}

```{r echo=FALSE}
diffplot(subset(changsha.diff.figure, tone == "T4"))
```

:::
::::

\

## Changsha combined

The above four figures are combined with the same f0 range on y-axis.

```{r include=FALSE}
remove_y <- theme(
  axis.title.y = element_blank()
  # axis.ticks.y = element_blank(),
  # axis.text.y = element_blank()
)
changsha.raw <- rawplot(changsha.raw.figure) + theme(strip.text.y = element_blank())
changsha.diff <- diffplot(changsha.diff.figure) + remove_y
```


:::: {style="display: grid; grid-template-columns: 1fr 1fr; grid-column-gap: 10px;"}
::: {}

```{r echo=FALSE}
changsha.raw
```
:::

::: {}

```{r echo=FALSE}
changsha.diff
```

:::
::::

